The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-06-22 analysis/paper/paper.qmd
Remove statement on the absence of theses from 2007
Create ngrams function

In order to describe the legacy of the EMU program, including the distinctive features of its didactic approach, this paper aims to reveal the main topics taught in it and how those topics had evolved through the years of the program. To that end, we employed a text mining approach in which we analysed its output: `r nrow(all_theses)` theses with an average of `r mean(str_length(emu_theses$text_clean), na.rm = TRUE)` words produced over the years for the duration of the program between `r paste0(min(all_theses$grad_year, na.rm = TRUE), "-", max(all_theses$grad_year, na.rm = TRUE))`. The first year of the program was not represented, as PDF files were only available from 2008 onward.

@@

## TO DO: generalise bigrams and trigrams into ngrams function

## Bigrams
emu_theses_bigrams <- emu_theses |> 
  unnest_tokens(bigram, text, token = "ngrams", n = 2) |> 
  separate(bigram, into = c("first", "second"), sep = " ", remove = FALSE) |> 
  anti_join(stop_words, by = c("first" = "word")) |> 
  anti_join(stop_words, by = c("second" = "word")) |> 
  filter(str_detect(first, "[a-z]") & 
         str_detect(second, "[a-z]"))

@@

bigram_counts

## Trigrams
emu_theses_trigrams <- emu_theses |> 
  unnest_tokens(trigram, text, token = "ngrams", n = 3) |> 
  separate(trigram, into = c("first", "second", "third"), sep = " ", remove = FALSE) |> 
  filter(!first %in% stop_words$word,
         !second %in% stop_words$word,
         !third %in% stop_words$word) |>  
  filter(str_detect(first, "[a-z]"), 
         str_detect(second, "[a-z]"),
         str_detect(third, "[a-z]"))

trigram_counts <- emu_theses_trigrams |> 
  count(first, second, sort = TRUE)

@@

## Bigram tf-idf
bigram_tf_idf <- emu_theses_bigrams |> 
  count(title, bigram) |> 
  bind_tf_idf(bigram, title, n) |> 
  arrange(desc(tf_idf))

@@

## Trigram tf-idf
trigram_tf_idf <- emu_theses_trigrams |> 
  count(title, trigram) |> 
  bind_tf_idf(trigram, title, n) |> 
  arrange(desc(tf_idf))

@@

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE, arrow = a) +
  geom_node_point(color = "lightblue", size = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()

@@

emu_theses_bigrams_top <- emu_theses_bigrams |>
  group_by(title) |>
  count(bigram, sort = TRUE) |>
  slice_max(n, n = 20) |>        ### top_n is superseded; better use slice_max instead
  # filter(n > 50)                ### filter words with a minimum count
  ungroup() |>
  mutate(bigram = reorder(bigram, n))

emu_theses_bigrams_top_all <- emu_theses_bigrams |>
  count(bigram, sort = TRUE) |>
  slice_max(n, n = 20) |>        ### top_n is superseded; better use slice_max instead
  # filter(n > 50)                ### filter words with a minimum count
  mutate(bigram = reorder(bigram, n))

emu_theses_bigrams_top |>
  filter(title == unique(title)[1:6]) |> 
  ggplot(aes(x = bigram, y = n, fill = title)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  labs(y = "Count",
       x = "Unique words",
       title = "Count of unique words found in thesis",
       subtitle = "Stop words were removed from the list") +
  facet_wrap( ~ title, scales = "free", ncol = 2) +
  theme(legend.position = "none") 
```

>>>>

In order to describe the legacy of the EMU program, including the distinctive features of its didactic approach, this paper aims to reveal the main topics taught in it and how those topics had evolved through the years of the program. To that end, we employed a text mining approach in which we analysed its output: `r nrow(all_theses)` theses with an average of `r mean(str_length(emu_theses$text_clean), na.rm = TRUE)` words produced over the years for the duration of the program between `r paste0(min(all_theses$grad_year, na.rm = TRUE), "-", max(all_theses$grad_year, na.rm = TRUE))`.

@@

## Add lemmas as optional column to ngram function

## Bigrams
emu_theses_bigrams <- emu_theses |> 
  get_ngrams(n = 2, title_col = "title", text_col = "text_clean", stem = TRUE)

emu_theses_bigrams |>
  dplyr::mutate(first_lemma =  |> tidytext::unnest_tokens())

spacyr::spacy_parse(emu_theses_bigrams$first)

@@

bigram_stem_counts <- emu_theses_bigrams |> 
  count(first_stem, second_stem, sort = TRUE)

bigram_counts
bigram_stem_counts

## Trigrams
emu_theses_trigrams <- emu_theses |> 
  get_ngrams(n = 3, title_col = "title", text_col = "text")

trigram_counts <- emu_theses_trigrams |> 
  count(first, second, third, sort = TRUE)

@@

## Bigram tf-idf
bigram_tf_idf <- emu_theses_bigrams |> 
  count(title, ngram) |> 
  bind_tf_idf(ngram, title, n) |> 
  arrange(desc(tf_idf))

@@

## Trigram tf-idf
trigram_tf_idf <- emu_theses_trigrams |> 
  count(title, ngram) |> 
  bind_tf_idf(ngram, title, n) |> 
  arrange(desc(tf_idf))

@@

ggraph(bigram_graph, layout = "fr") +
  geom_edge_link(aes(edge_alpha = n), show.legend = FALSE, arrow = a) +
  geom_node_point(color = "lightblue", linewidth = 5) +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1) +
  theme_void()

@@

emu_theses_bigrams_top <- emu_theses_bigrams |>
  group_by(title) |>
  count(ngram, sort = TRUE) |>
  slice_max(n, n = 20) |>        ### top_n is superseded; better use slice_max instead
  # filter(n > 50)                ### filter words with a minimum count
  ungroup() |>
  mutate(bigram = reorder(ngram, n))

emu_theses_bigrams_top_all <- emu_theses_bigrams |>
  count(ngram, sort = TRUE) |>
  slice_max(n, n = 20) |>        ### top_n is superseded; better use slice_max instead
  # filter(n > 50)                ### filter words with a minimum count
  mutate(ngram = reorder(ngram, n))

emu_theses_bigrams_top |>
  filter(title == unique(title)[1:10]) |> 
  ggplot(aes(x = ngram, y = n, fill = title)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  labs(y = "Count",
       x = "Unique words",
       title = "Count of unique words found in thesis",
       subtitle = "Stop words were removed from the list") +
  facet_wrap( ~ title, scales = "free", ncol = 2) +
  theme(legend.position = "none") 
```
